%
% Copyright © 2012 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%
%
\mychapter{Professor Poppitz's handouts.}
   \input{poppitz.tex}
%
\mychapter{Tensor and geometric algebra comparisons.}
   \input{problems/antisymmetricTensorTx}
%
\mychapter{Frequency four vector.}
\index{frequency!four vector}
   \input{lectures/relativisticElectrodynamicsT1Aside.tex}
%
\mychapter{Non-inertial (local) observers.}
\index{local observer}
   \input{lectures/relativisticElectrodynamicsT2_2.tex}
%
\mychapter{3D GPS geometries.}
\index{GPS}
   \input{problems/relElectroDynProblemSet1GPSspherical.tex}
%
\mychapter{Complex notation for plane relativistic applications.}
   \input{problems/complexPlanarBoost}
%
%
% what I have marked as T4 was really T5.  T4 was the fun with tensors
% stuff that was part of the ungraded portion of the problem set.
%
\mychapter{Waveguides: confined EM waves.}
\index{waveguide}
   \input{lectures/relativisticElectrodynamicsT4.tex}
%
\mychapter{3D divergence for parametrized volume element.}
   \input{problems/divergence3Dtensor}
%
\mychapter{EM fields from magnetic dipole current.}
\index{magnetic dipole}
   \input{lectures/relativisticElectrodynamicsT8.tex}
%
\mychapter{Yukawa potential note.}
\index{Yukawa potential}
   \input{lectures/relativisticElectrodynamicsT8_2.tex}
%
\mychapter{Proof of the d'Alembertian Green's function.}
\index{d'Alembertian}
   \input{lectures/relativisticElectrodynamicsL18_deLambertianGreens.tex}
%
\iftoggle{print-version}{}
{
\mychapter{Mathematica notebooks.}
\index{Mathematica}
   \input{mathematica.tex}
}
